\chapter{Curriculum Vitae}

\begin{table}[h]
\centering
\begin{tabular}{rl}
Surname, given name: & Király, Péter \\
Address:             & Im Winkel 26, 37077 Göttingen, Germany \\
E-mail:              & peter.kiraly@gwdg.de \\
\end{tabular}
\end{table}

Profiles on the web: GitHub\footnote{\url{https://github.com/pkiraly/}}, Google Scholar\footnote{\url{https://scholar.google.de/citations?user=hvoZFusAAAAJ&hl=en}}, ORCID\footnote{\url{https://orcid.org/0000-0002-8749-4597}}, ResearchGate\footnote{\url{https://www.researchgate.net/profile/Peter_Kiraly3}}, Academia.edu\footnote{\url{https://uni-goettingen.academia.edu/PeterKiraly}}, LinkedIn\footnote{\url{http://www.linkedin.com/in/peterkiraly}}, SlideShare\footnote{\url{http://www.slideshare.net/pkiraly}}, Twitter\footnote{\url{https://twitter.com/\#!/kiru}}

\emph{University education}

1990-1996:	Diploma in History and Textual Studies, University of Miskolc, Hungary

\emph{Skills}

\begin{itemize}
 \setlength{\parskip}{0pt}
 \setlength{\itemsep}{0pt plus 1pt}
\item languages: Hungarian (native), English (working level proficiency), Latin (intermediate), German (beginner), Dutch (beginner)
\item Librarian and Archival skills (focusing on descriptive standards)
\item Researching historical documents (including textual studies)
\item Computer Science -- Web
\item Computer Science -- Programming
\item Computer Science -- Data Science
\end{itemize}

\emph{Employment history}

\begin{itemize}
 \setlength{\parskip}{0pt}
 \setlength{\itemsep}{0pt plus 1pt}
\item 2014 October-: Gesellschaft für wissenschaftliche Datenverarbeitung mbH Göttingen (GWDG) as scientific co-worker, software developer
\item 2012-2014 September: Europeana.eu as Portal Backend Developer
\item 2008-2013: eXtensible Catalog Project (from 2010 eXtensible Catalog Organisation) as software developer (from 2012 in part time)
\item 2007-2010: Hungarian Academy of Science - Eötvös Loránd University's Online Critical Editing special research group (part-time job)
\item 2005-2008: Tesuji S.r.l., Tesuji Hungary Ltd. (Italy-Hungary) as Java developer
\item 2001-2005: Arcanum Database Ltd. (Hungary) as web publication developer, editor
\item 1998-2000: National Széchényi Library (Hungary) as manuscript librarian
\item 1996-1998: Budapest City Archives (Hungary) as archivist
\end{itemize}

\emph{Voluntary works}
\begin{itemize}
 \setlength{\parskip}{0pt}
 \setlength{\itemsep}{0pt plus 1pt}
\item 2017-: organizer of Göttingen Data Science Meetup team
\item 2016-: member of Europeana Data Quality Committee\footnote{\url{https://pro.europeana.eu/project/data-quality-committee}}
\item 2015-: member of The Code4Lib Journal editorial team\footnote{\url{http://journal.code4lib.org}}
\item 2015-2017: board member of Göttingen Dialogue in Digital Humanities
\item 2012-2014: member of W3C Schema Bib Extend Community Group
\item 2008-2014: active member of Drupal community
\item 1995-: volunteer of Hungarian Electronic Library\footnote{\url{https://mek.oszk.hu}}
\end{itemize}

\emph{Conference presentations and publications in the context of this thesis}

\begin{enumerate}
  \setlength{\parskip}{0pt}
  \setlength{\itemsep}{0pt plus 1pt}
\item \emph{Multilinguality of Metadata. Measuring the Multilingual Degree of Europeana‘s Metadata}\footnote{slides: \url{http://doi.org/10.13140/RG.2.2.30771.43047}} International Symposium on Information Science, Berlin, 2017. March 13-15. Presentation together with Juliane Stiller. Paper was published as \cite{stiller-kiraly2017}
\item \emph{Measuring metadata quality. A quick overview in the context of Europeana metadata}\footnote{\url{http://doi.org/10.13140/RG.2.2.36780.67207}} \#dariahTeach, Lausanne, 2017. March 23-24. Poster
\item \emph{Multilinguality of Metadata. Measuring the Multilingual Degree of Europeana's Metadata} SI \& IT Workshop, Göttingen, 2017. May 10. Presentation together with Juline Stiller
\item \emph{Measuring Metadata Quality and the Europeana use case}\footnote{slides: \url{http://bit.ly/metadata-ldq4}} Linked Data Quality workshop 2017, Portorož, 2017. May 29. Invited keynote speech
\item \emph{Towards an extensible measurement of metadata quality}\footnote{slides: \url{http://bit.ly/way2datech}} DATeCH 2017, Göttingen, 2017 June 1-2. Paper published as \cite{kiraly2017}
\item \emph{``Nothing is created, nothing is lost, everything changes''. Measuring and visualizing data quality in Europeana.}\footnote{slides: \url{http://bit.ly/mq-elag2017}} ELAG 2017, Athens, 2017. June 6-9. Presentation together with Valentine Charles
\item \emph{Measuring completeness as metadata quality metric in Europeana}\footnote{slides: \url{http://bit.ly/mq-dh2017}} Digital Humanities 2017, Montréal, 2017 August 7-11. Extended abstract was published in the Digital Humanities 2017 Conference Abstracts\footnote{\url{https://dh2017.adho.org/abstracts/DH2017-abstracts.pdf}}, cited by \cite{khan2018}.
\item Linked Data Quality Workshop Semantics 2017, Amsterdam, 2017. September 14 -- as organizer and presenter.
\item \emph{Evaluating Data Quality in Europeana: Metrics for Multilinguality} (Meta)-Data Quality Workshop (part of TPDL 2017), Thessaloniki, 2017. September 17-21. Presented by Juliane Stiller, the paper was published as \cite{charles2017}.
\item \emph{Measuring Metadata Quality in Europeana}\footnote{\url{http://bit.ly/adochs-europeana}} and \emph{Measuring library catalogs}\footnote{\url{http://bit.ly/adochs-marc}} ADOCHS meeting, Brussels, 2017 November 21
\item LDCX at Stanford University, 2018 March. Leading workshop and presentation.
\item \emph{Data Quality Workshop}\footnote{\url{http://bit.ly/elag2018-data-quality-workshop}} ELAG 2018, Prague, 2018 June 5-7. Workshop together with Anette Strauch and Patrick Hochstenbach with contribution from Mark Phillips\footnote{Mark Philipps: ``UNT Libraries Metadata Quality Interfaces'' (video) \url{https://www.youtube.com/watch?v=ATM3EwixnW8}}.
\item \emph{Evaluating Data Quality in Europeana:
Metrics for Multilinguality}. MTSR 2018. 12th International Conference on Metadata and Semantics Research, Limassol, 2018 Oct 23-26. Presentation together with Juliane Stiller. Paper published as \cite{kiraly-et-al2018}.
\item \emph{Researching metadata quality}\footnote{slides: \url{http://bit.ly/qa-orkg2018}}. Open Research Knowledge Graph workshop, Hannover, 2018 November 22.
\item \emph{Metadata quality in cultural heritage institutions}\footnote{slides: \url{http://bit.ly/qa-relres-fair}} ReIReS (Research Infrastructure on Religious Studies) Workshop on FAIR Principle for Digital Research Data Management, Mainz, 2018 November 28.
\item \emph{Measuring Completeness as Metadata Quality Metric in Europeana}\footnote{slides: \url{http://bit.ly/qa-cas2018}} Computational Archival Science workshop (part of IEEE Big Data 2018), Seattle, 2018 December 10-13. Paper published as \cite{kiraly2018}.
\item \emph{Adat a könyvtárban} (Data in the library -- paper in Hungarian about the changing status of data in LAM). In Hagyomány és újitás a 21. századi könyvtárban (Erdélyi Évszázadok. A Koloszvári Magyar Történeti Intézet Évkönyve. III.) eds. Rüsz-Fogarasi Enikő, Monok István. Kolozsvár (Romania), 2018. pp. 49-74.
\end{enumerate}
